A performance assessment of evolutionary algorithms in a volunteer computing system

### 2016-03-12 PPSN2016/paper.Rnw
Explaining the table

Every run had slightly different conditions, although in some cases it
was just a server reboot and a new round of announcements. Each run
batch included at least 30 competions, that is, running until the
solution was found. The number of runs was controlled by polling an
URL that indicated the number of runs made in the present batch so
far. A summary of the experiments and  its results is shown in Table
\ref{tab:runs}. This table shows the median time needed to find the
solution as well as the median number of IPs and PUTs.

>>>>

Every run had slightly different conditions, although in some cases it
was just a server reboot and a new round of announcements. Each run
batch included at least 30 competions, that is, running until the
solution was found. The number of runs was controlled by polling an
URL that indicated the number of runs made in the present batch so
far. A summary of the experiments and  its results is shown in Table
\ref{tab:runs}. This table shows the median time needed to find the
solution as well as the median number of IPs and PUTs. In this case we
distinguish between the total number of clients participating in that
particular run, and the {\em actual} number whose contributions were
accepted into the cache, which was set up to accept those only if {\em
  new} chromosomes were sent to the server in order to avoid overlaps
between one run and the next. That is why, in both cases, the
``Contributing'' column includes a value that is less than the total
number. The final column includes the total number of runs in that
particular batch, finished after a minimum number of 30 was reached.
